---
title: "linear_model"
author: "ww2745"
date: "2024-11-07"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

```

Do some data cleaning
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location/2) |> 
  rename(
    borough= neighbourhood_group,
    neighbourhood=neighbourhood
  ) |> 
  filter(
    borough != "Staten Island"
  ) |> 
  select(price, stars, neighbourhood, borough, room_type) |> 
  mutate(
    borough= fct_infreq(borough) ##not in alphabet order but with freq order
  )
```

#Fit some models

Start relatively simple.
```{r}
fit = lm(price~stars, data=nyc_airbnb)

summary(fit)

names(summary(fit))

coef(fit)

broom::tidy(fit) ##can do it with tibble, samilar things with coef

fit |> 
  broom::tidy() |> 
  select(term, estimate, p.value)
```

Try a bit more complex.

```{r}
fit=
  lm(price ~ stars + borough, data=nyc_airbnb)

fit |> 
  broom::tidy() |> 
  select(term, estimate, p.value) |> 
  mutate(
    term = str_replace(term, "borough","Borough:")
  ) |> 
  knitr::kable(digits=3)
```

## Some diagnostics

(backtrack to some EDA)

```{r}
nyc_airbnb |> 
  ggplot(aes(x=stars,y=price))+
  geom_point()+
  stat_smooth(method="lm")
```


Most diagnostics use residuals

```{r}
modelr::add_residuals(nyc_airbnb,fit) |> 
  ggplot(aes(x=resid))+
  geom_histogram()
```

```{r}
modelr::add_residuals(nyc_airbnb,fit) |> 
  ggplot(aes(x=borough, y=resid))+
  geom_violin()+
  ylim(-200,500) ##very screwed residuals
```

Residuals against fitted values

@@@
```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  modelr::add_predictions(fit) |> 
  ggplot(aes(x=pred, y=resid))+
  geom_point()
```

## Hypothesis testing

```{r}
fit |> 
  broom::tidy()
```


```{r}
fit_null=lm(price~stars+borough, data=nyc_airbnb)
fit_alt=lm(price~stars+borough+room_type, data=nyc_airbnb)
```

Look at both
```{r}
fit_null |> 
  broom::tidy()

fit_alt |>
  broom::tidy()

anova(fit_null, fit_alt) |> 
  broom::tidy()
```

## Do effects differ across boroughs

First, use a lot of interactions

```{r}
nyc_airbnb |> 
  lm(price~stars*borough+room_type*borough, data=_) |> 
  broom::tidy()
```

Could just fit separate models.

```{r}
nyc_airbnb |> 
  filter(borough=="Manhattan") |> 
  lm(price~stars+room_type, data=_) |> 
  broom::tidy()
```

Get fancy and use list columns.

```{r}
nyc_airbnb |> 
  nest(data= -borough) |> 
  mutate(
    model= map(data, \(x) lm(price~stars+room_type, data = x)),
    results = map(model, broom::tidy) ##same with previous block
  ) |> 
  select(borough, results) |>  ## table rearrangement
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from= estimate ##want to compare
  )
```

what about room type across manhattan neighbourhood?

```{r}
nyc_airbnb |> 
  filter(
    borough=="Manhattan",
    neighbourhood=="Chinatown") |> 
  lm(price~stars+room_type, data=_) |> 
  broom::tidy()
  
```

Let's do this for all neighbourhoods!

```{r}
manhattan_neighborhood_fit_df=
  nyc_airbnb |> 
    filter(borough=="Manhattan") |> 
    nest(data=-(borough:neighbourhood)) |> 
    mutate(
      model = map(data, \(x) lm(price~stars+room_type, data=x)),
      results=map(model, broom::tidy)
    ) |> 
    select(neighbourhood, results) |> 
    unnest(results)
```

look at the effect of room type
```{r}
manhattan_neighborhood_fit_df |> 
  filter(str_detect(term, "room_type")) |> 
  ggplot(aes(x=term, y =estimate))+
  geom_boxplot()
```

```{r}
manhattan_neighborhood_fit_df |> 
  filter(str_detect(term,"room_type")) |> 
  filter(estimate>0)

nyc_airbnb |> 
  filter(
    neighbourhood =="Noho",
    room_type=="Shared room"
  )
```

if you need to do logistic regression,use glm(), and need to tell the distribution,eg. family=binomial()